---
title: "01_toy"
author: "randy"
date: '2022-04-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# clear the entire environment
rm(list = ls())

# clear all data frames from environment
rm(list=ls(all=TRUE)[sapply(mget(ls(all=TRUE)), class) == "data.frame"])

# clear all lists from environment
rm(list=ls(all=TRUE)[sapply(mget(ls(all=TRUE)), class) == "list"])
```


```{r}
library(pheatmap)

devtools::load_all()
# check()
```

First, let's look at the default `Xsim()` results

```{r}
subject_sim = 100
num_leaf = 20
covariates_sim = 20
rho = 0.2
num_cov = 15
seed = 222
num_branch = 18


Xmat <- Xsim(subject_sim = subject_sim, 
             # tree = NULL,
             num_leaf = num_leaf,
             covariates_sim = covariates_sim,
             rho = rho,
             # Sigma = NULL,
             num_cov = num_cov, 
             seed = seed)
str(Xmat)

(X0 <- Xmat$X)
(I0 <- Xmat$zeta)
```



```{r}
## we can always manually 
Xmat$zeta <- matrix(1, nrow = 6, ncol = 10)
dim(X0); dim(I0)


# Xmat$zeta <- matrix(1, nrow = 6, ncol = 10)
dim(X0); dim(I0)

tree0 <- Xmat$tree
phytools::plotTree(tree0, node.numbers = T)
```


Now we have the working design matrix $X^*$, this is the $X$ by removing the first column;
and the $\zeta^*$ matrix now must include the first column of 1s.


```{r}
Xstar <- Xmat$X[, -1]
Xmat$zeta <- rbinom(38 * 20, 
                    size = 1, 
                    0.1) %>%
  matrix(nrow = 38, ncol = 20)
Xmat$zeta[, 1] <- 1
```



```{r}
data_dtm <- simulate_DTM(subject_sim = subject_sim,
                        tree = Xmat$tree,
                        num_leaf = num_leaf,
                        covariates_sim = covariates_sim,
                        rho = 0.2,
                        X = Xmat$X,
                        zeta_sim = Xmat$zeta,
                        rep = 5,
                        num_cov = num_cov,
                        phi_min = 0.9,
                        phi_max = 1.2,
                        seed = seed)

str(data_dtm)
```


first of all check whether the tree created earlier and the tree used are the same;


The tree is the same; also it has `r num_leaf` tips and `r num_branch` branches, 
so to the end, the final $\zeta$ and $\beta$ matrix will have `r num_branch + num_leaf` rows.

because we have `r num_cov` but with the first colunm as random intercept, 
the final $\beta$ will be a `r num_cov - 1` $\times$ `r num_cov` matrix;


```{r}
phytools::plotTree(Xmat$tree, node.numbers = T)
phytools::plotTree(data_dtm$tree, node.numbers = T)
```

## check the structure of the outcomes.

```{r}
str(data_dtm)
# View(data_dtm$X)

# print(data_dtm$Y)
# print(data_dtm$zeta)
# print(data_dtm$phi_sim)
# View(data_dtm$phi_sim)
# View(data_dtm$zeta_sim)
# View(data_dtm$phi_sim %*% t(data_dtm$zeta_sim))
```


The final $\beta$ will be the original one by removing the first column.
the final $\beta$ will be a `r num_cov - 1` $\times$ `r num_cov` matrix;

```{r fig.height=3, fig.width=1.5}
betas0 <- data_dtm$phi_sim


colors <- c(colorRampPalette(c("green", "black"), bias = 2)(100),
            colorRampPalette(c("black", "red"), bias = 2)(100))


pheatmap(
  mat = as.matrix(betas0), 
  color = colors,
  ## colors from line86
  border_color = "grey60",
  cluster_rows = F,  
  cluster_cols = F,
  show_colnames = T,
  show_rownames = T,
  drop_levels = F,
  fontsize = 10,
  frontsize_row = 8,
  frontsize_col = 8,
  main  = "Heatmap default betas")

# pheatmap(
#   mat = as.matrix(data_dtm$Y[[1]]), 
#   color = colorRampPalette(c("black", "red"), bias = 2)(100),
#   ## colors from line86
#   border_color = "grey60",
#   cluster_rows = F, 
#   cluster_cols = F, 
#   show_colnames = T,
#   show_rownames = T,
#   drop_levels = F,
#   fontsize = 10,
#   frontsize_row = 8,
#   frontsize_col = 8,
#   main  = "Heatmap Clustered")
```


```{r}
Design <- data_dtm$X[, -1]
beta <- data_dtm$phi_sim[, -1]


# save(Design, beta, file = "simulated_00_data.csv")
```






